### 2019-03-27 README.Rmd
build pkgdown
update docs

```{r}
library(taxadb)
library(dplyr)
library(readr)
```

@@

>>>>

```{r message = FALSE}
library(taxadb)
library(dplyr)
library(readr)
```

@@

## Learn more

See richer examples, including name cleaning and background on the schema in the vignettes:

- [Tutorial](https://cboettig.github.io/taxadb/articles/intro.html)
- [Schema](https://cboettig.github.io/taxadb/articles/articles/schema.html)
